### 2025-05-13 Chapters/Chapter2.tex
Updated final image. Think this is done.

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.6]{Figures/MAEoverIceland.png}
  \caption[MAE distribution by station]{Distribution of mean absolute error (MAE) by station for all observed wind speeds. Image is missing units for MAE, which is in m/s.}
  \label{fig:station_mae_distribution}
\end{figure}

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.7]{Figures/mae_by_stations.png}
  \caption[MAE distribution by station]{Distribution of mean absolute error (MAE) by station for all observed wind speeds.}
  \label{fig:station_mae_distribution}
\end{figure}
